### 2023-06-05 README.Rmd
generalized doprojections and getdata to allow for proper use of startCE.
Minor changes to allow for consthcr scenarios. Vignettes need fixing.

>>>>

* 2023-06-04 aMSE 0.1.4 Small modifications to generalize across jurisdicitons and allow for the consthcr constant catch harvest strategy; also removed irrelavent messages when plotting the phase plot

* 2023-06-03 aMSE 0.1.3 Modified to allow the mcdahcr and constrefhcr HCR to run successfully with the conditioned SA setup.
